\bf Forecast Reconciliation: A geometric view with new insights on bias correction.

### 2019-08-31 Hierarchical-forecast-reconciliation/HierarchicalForecastReconciliation.tex
changed summary at end of intro

	The remainder of this paper is structured as follows. Section~\ref{sec:CoheForecasts} deals with the concept of coherence and defines so called hierarchical time series in a way that does not depend on any notion of bottom-level series.  Section~\ref{sec:Reconciliation} defines forecast reconciliation in terms of projections and includes a proof that reconciled forecasts dominate base forecasts with respect to a specific loss function. In Section~\ref{sec:BiasInRecon} we prove the unbiasedness preserving property of reconciliation via certain projection matrices and propose methods for bias correction. In Section \ref{sec:EmpStudy} we evaluate these methods for in an extensive emprirical application to domestic tourism flow in Australia.  Section~\ref{sec:conclusions} concludes with some discussion and thoughts on the  future of research in forecast reconciliation.
\section{Coherent forecasts}\label{sec:CoheForecasts}

@@

	\begin{subfigure}[t]{0.45\textwidth}
%		\centering
		\input{Figs/OrthProj}
		%			\label{fig:OrthProj}
	\end{subfigure}
	\hspace{1cm}
	\begin{subfigure}[t]{0.45\textwidth}
%		\centering
		\input{Figs/ObliqProj}
		%			\label{fig:ObliqProj}
	\end{subfigure}

>>>>

	The remainder of this paper is structured as follows. Section~\ref{sec:CoheForecasts} deals with the concept of coherence and defines so called hierarchical time series in a way that does not depend on any notion of bottom-level series.  Section~\ref{sec:Reconciliation} defines forecast reconciliation in terms of projections and includes a proof that reconciled forecasts dominate base forecasts with respect to a specific loss function. In Section~\ref{sec:BiasInRecon} we prove the unbiasedness preserving property of reconciliation via certain projection matrices and propose methods for bias correction. In Section \ref{sec:EmpStudy} we conduct an extensive empirical application to domestic tourism flow in Australia with two objectives; first to demonstrate the theorems discussed in~\ref{sec:Reconciliation}, second to evaluate the methods for bias correction discussed in~\ref{sec:BiasInRecon}.  Section~\ref{sec:conclusions} concludes with some discussion and thoughts on the  future of research in forecast reconciliation.
\section{Coherent forecasts}\label{sec:CoheForecasts}

@@

	\begin{subfigure}[t]{0.45\textwidth}
%		\centering
		\input{Figs/Orthproj}
		%			\label{fig:OrthProj}
	\end{subfigure}
	\hspace{1cm}
	\begin{subfigure}[t]{0.45\textwidth}
%		\centering
		\input{Figs/ObliqProj}
		%			\label{fig:ObliqProj}
	\end{subfigure}
